\mythesistitleNOTSYNPOSIS

### 2013-04-12 src/030chap3.tex
corrected an error in lemma lem:priv-card

\begin{lemma}
  \label{lem:4-way}
  Let $(\cF, \cl)$ be an \ICPPL and $\cl(S_i)=P_i$, $S_i \in \cF$, $1
  \leq i \leq 4$.  Then, $|\cap_{i=1}^4 S_i| = |\cap_{i=1}^4 P_i|$.
\end{lemma}
\begin{proof}
  Consider the set of set intersections with $S_1$ $\cF' = \{S_2 \cap S_1, S_3
  \cap S_1, S_4 \cap S_1\}$ and let $\cl'$ be a tree path labeling of
  $\cF'$ such that $\cl'(S_i \cap S_1) = P_i \cap P_1, 2 \le i \le
  4$. Clearly, $P_2 \cap P_1$, $P_3 \cap P_1$, and $P_4 \cap P_1$ are
  subpaths of path $P_1$, thus equivalent to intervals.  Due to the
  three way intersection cardinality preservation property of the
  ICPPL $(\cF, \cl)$, this new tree path labeling $(\cF', \cl')$
  preserves pairwise intersection cardinalities.  Now by applying
  Lemma~\ref{lem:intersection-cardinality} to the sets in $\cF'$ and
  their corresponding path images due to $\cl'$, it follows that
  $|\cap_{i=1}^4 S_i| =| \cap_{i=1}^4 P_i|$.
\end{proof}
\begin{corollary} 
  \label{corr:4-way} 
  Let $(\cF, \cl)$ be an \ICPPL and $\cl(S_i)=P_i$, $S_i \in \cF$, $1
  \leq i \leq 4$. If $P_i$, $1
  \leq i \leq 4$ are such that $P_1 \cap P_2$, $P_1
  \setminus P_2$, $P_2 \setminus P_1$ are also paths, then:
  \begin{align*}
   |(S_1 \setminus S_2) \cap S_3 \cap S_4| &= |(P_1 \setminus P_2) \cap P_3 \cap P_4|\\
   |(S_2 \setminus S_1) \cap S_3 \cap S_4| &= |(P_2 \setminus P_1) \cap P_3 \cap P_4| 
  \end{align*}
\end{corollary}
\begin{proof}
  It is clear that $|(P_1 \setminus P_2) \cap P_3 \cap P_4| =
  |\displaystyle \cap_{i=1}^4 P_i| - | P_2 \cap P_3 \cap P_4|$.  Since
  we have an ICPPL, from Lemma~\ref{lem:4-way}, it follows that the
  intersection cardinalities are preserved.
\end{proof}
\begin{lemma}
  \label{lem:priv-card}
  Let $(\cF, \cl)$ be an \ICPPL and $\cl(S) = P$ for some $S \in \cF$.  If sets
  $S_{priv}$ and $P_{priv}$ contain only those elements of $S$ and $P$
  that occur in no set other than $S$ and $P$, respectively, then
  $|S_{priv}|=|P_{priv}|$.
\end{lemma}
\begin{proof}
  Consider the set system $ \cF' = \{S_i \cap S \mid S_i \in \cF, i
  \in [n]\}$ and path labeling $\cl'(S_i \cap S) = P_i \cap P$.  Since
  $(\cF, \cl)$ is an \ICPPL, it can be easily verified that $(\cF',
  \cl')$ is an ICPIA on path (interval) $P$.  Let $S_{two}$ and
  $P_{two}$ be the elements of $S$ and $P$ which are in one {\em
    other} set and path, respectively \ie $S_{two} = S \cap (\cup_{S_i
    \ne S} S_i)$ and $P_{two}$ is defined analogously. It may be noted
  that $S_{two} = \supt{\cF'}$ and $P_{two} = \supt{\cF'^{\cl'}}$.
  From Lemma~\ref{lem:icpia} it follows that there is a bijection
  $\phi$ from $S_{two}$ to $P_{two}$ such that for each $i$, the image
  of $S_i \cap S$ under $\phi$ is $P_i \cap P$ (definition of
  feasibility).  Moreover, this means $|S_{two}| = |P_{two}|$. By
  definition, $S_{priv} = S \setminus S_{two}$ and $P_{priv} = P \setminus P_{two}$.
  Thus $|S_{priv}| = |S \setminus S_{two}| = |P \setminus
  P_{two}|=|P_{priv}|$.  
\end{proof}

>>>>

\begin{lemma}
  \label{lem:4-way}
  Let $(\cF, \cl)$ be an \ICPPL and $\cl(S_i)=P_i$, $S_i \in \cF$, $1
  \leq i \leq 4$.  Then, $|\cap_{i=1}^4 S_i| = |\cap_{i=1}^4 P_i|$.
\end{lemma}
\begin{proof}
  Consider the set of set intersections with $S_1$ $\cF' = \{S_2 \cap S_1, S_3
  \cap S_1, S_4 \cap S_1\}$ and let $\cl'$ be a tree path labeling of
  $\cF'$ such that $\cl'(S_i \cap S_1) = P_i \cap P_1, 2 \le i \le
  4$. Clearly, $P_2 \cap P_1$, $P_3 \cap P_1$, and $P_4 \cap P_1$ are
  subpaths of path $P_1$, thus equivalent to intervals.  Due to the
  three way intersection cardinality preservation property of the
  ICPPL $(\cF, \cl)$, this new tree path labeling $(\cF', \cl')$
  preserves pairwise intersection cardinalities.  Now by applying
  Lemma~\ref{lem:intersection-cardinality} to the sets in $\cF'$ and
  their corresponding path images due to $\cl'$, it follows that
  $|\cap_{i=1}^4 S_i| =| \cap_{i=1}^4 P_i|$.
\end{proof}
\begin{corollary} 
  \label{corr:4-way} 
  Let $(\cF, \cl)$ be an \ICPPL and $\cl(S_i)=P_i$, $S_i \in \cF$, $1
  \leq i \leq 4$. If $P_i$, $1
  \leq i \leq 4$ are such that $P_1 \cap P_2$, $P_1
  \setminus P_2$, $P_2 \setminus P_1$ are also paths, then:
  \begin{align*}
   |(S_1 \setminus S_2) \cap S_3 \cap S_4| &= |(P_1 \setminus P_2) \cap P_3 \cap P_4|\\
   |(S_2 \setminus S_1) \cap S_3 \cap S_4| &= |(P_2 \setminus P_1) \cap P_3 \cap P_4| 
  \end{align*}
\end{corollary}
\begin{proof}
  It is clear that $|(P_1 \setminus P_2) \cap P_3 \cap P_4| =
  |\displaystyle \cap_{i=1}^4 P_i| - | P_2 \cap P_3 \cap P_4|$.  Since
  we have an ICPPL, from Lemma~\ref{lem:4-way}, it follows that the
  intersection cardinalities are preserved.
\end{proof}
\begin{lemma}
  \label{lem:priv-card}
  Let $(\cF, \cl)$ be an \ICPPL and $\cl(S) = P$ for some $S \in \cF$.  If sets
  $S_{priv}$ and $P_{priv}$ contain only those elements of $S$ and $P$
  that occur in no set other than $S$ and $P$, respectively, then
  $|S_{priv}|=|P_{priv}|$.
\end{lemma}
\begin{proof}
  Consider the set system $ \cF' = \{S_i \cap S \mid S_i \in \cF, i
  \in [n]\}$ and path labeling $\cl'(S_i \cap S) = P_i \cap P$.  Since
  $(\cF, \cl)$ is an ICPPL, it can be easily verified that $(\cF',
  \cl')$ is an ICPIA on path (interval) $P$.  Let $S_{two}$ and
  $P_{two}$ be the elements of $S$ and $P$ which are in one {\em
    other} set and path, respectively i.e. $S_{two} = S \cap (\cup_{S_i
    \ne S} S_i)$ and $P_{two}$ is defined analogously. It may be noted
  that $S = \supt({\cF'})$ and $P = \supt({\cF'}^{\cl'})$.
  From Lemma~\ref{lem:icpia} it follows that there is a bijection
  $\phi$ from $S$ to $P$ such that for each $i$, the image
  of $S_i \cap S$ under $\phi$ is $P_i \cap P$ (definition of
  feasibility).  Moreover, this means that in $\phi$,
the elements of $S_{two}$ are mapped to the elements of $P_{two}$.  The proof is of this claim is by contradiction. Let us assume that there is an $x \in S_{two}$ is mapped to
a $v \in P_{priv}$ under $\phi$.  Since $x \in S_{two}$, let $S_i$ be another set that contains $x$, other than $S$.  Then it means that $\phi(S_i \cap S)$ which is same as $\cl'(S_i \cap S) =P_i \cap P$ contains $v$. This implies that $v \in P_i \cap P$, contradiction to the fact that $v \in P_{priv}$.  Therefore, under the bijection $\phi$, the image of the set $S_{two}$ is the set $P_{two}$.
Conseqently, it follows that $|S_{two}| = |P_{two}|$.  
By
  definition, $S_{priv} = S \setminus S_{two}$ and $P_{priv} = P \setminus P_{two}$.
  Thus $|S_{priv}| = |S \setminus S_{two}| = |P \setminus
  P_{two}|=|P_{priv}|$.  
\end{proof}
